---
title: "Lion Co-infection Networks"
author: "Erin Gorsich"
date: "January 13, 2016"
output: html_document
---

```{r, data_readin, include=FALSE}
###########################################################
# read in HB's data and packages and scripts code
###########################################################

# TAKE OUT OTHER, BABESIA AND THEILERIABABESIA

setwd("~/GitHub/lion-co-infection-networks")
alldata<-read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/COINCLIQ.csv")
dataneg<-alldata[alldata$FIV=="Negative",]
datapos<-alldata[alldata$FIV=="Positive",]
plotdata<-alldata[,c(11:35)]
library(lattice)  
library(bipartite)
library(igraph)  # tried bigraph but not avaliable
library(gplots)
library(HiveR)
 library(grid)
#####################
# Functions: There are three script files required to run this script
source("prep_data_to_matrix.R")   # functions that groom raw data into network matricies
source("calculate_net_and_node_stats.R")  # functions that calculate network statistics
source("make_bipart_hive_plot.R")   
source("mod.edge2HPD.R")
# see: Patterns of interactions of a large fish–parasite network in a tropical floodplain by Lima et al. 2012
```
##Summary statistics  
Plot of overall patogen prevalence ordered by type and prevalence
```{r, descriptive_stats, echo=FALSE}
get_prev<-function(dat) {length(dat[dat=="Positive"])/length(dat)}
temp<-apply(alldata[,c(11:35)], 2, get_prev)
gut = c("ASCARIDS", "TAPES", "HOOKS", "COCCIDIA", "TOXO", "WHIPS")
bloodborne = c("ERLICHIAANAPLASMA", #"THEILERIABABESIA", "BABESA", 
               "BFELIS", "BLEO", "BMICROTI", "BLENGUA", "TBICORNIS", 
               "HEPATOZOON", "TANNAE", "BCANIS", "BROSSI", "BVOGELI")
virus = c("FIV", "CDV", "FPV", "CALICI", "CORONA")

newdf<-data.frame(parasite=c(virus, gut, bloodborne), 
                  type=c(rep("virus", length(virus)), rep("gut", length(gut)), 
                         rep("bloodborne", length(bloodborne)) ), 
                  prev=NA, col= c(rep("darkseagreen", length(virus)), 
                                  rep("darksalmon", length(gut)), 
                                  rep("lightblue3", length(bloodborne))) )

for (i in 1:length(newdf$parasite)){
    temp<- alldata[,colnames(alldata) == as.character(newdf$parasite[i])]
    newdf$prev[i]<- length(temp[temp=="Positive"])/length(temp)
    rm(temp)
}
newdf$parasite<-as.character(newdf$parasite)
newdf$name<-newdf$parasite
newdf$name[newdf$name == 'ERLICHIAANAPLASMA']<-"ERLANAP"
newdf$name[newdf$name == 'HEPATOZOON']<-"HEPATO"

virus<-newdf[newdf$type=="virus",]
gut<-newdf[newdf$type=="gut",]
blood<-newdf[newdf$type=="bloodborne",]

par(mar=c(4,5,4,2)+0.1)
barplot2(height=c(virus$prev[order(virus$prev, decreasing=FALSE)], 
                  gut$prev[order(gut$prev, decreasing=FALSE)], 
                  blood$prev[order(blood$prev, decreasing=FALSE)]), 
         names.arg=c(as.character(virus$name[order(virus$prev, decreasing=FALSE)]), 
                  as.character(gut$name[order(gut$prev, decreasing=FALSE)]), 
                  as.character(blood$name[order(blood$prev, decreasing=FALSE)])),
         col=c(as.character(virus$col[order(virus$prev, decreasing=FALSE)]), 
                  as.character(gut$col[order(gut$prev, decreasing=FALSE)]), 
                  as.character(blood$col[order(blood$prev, decreasing=FALSE)])),
         horiz=TRUE, las=1, cex.names = 0.8)
```


Plot of prevalence in FIV+ and FIV- lions.
Visually, we can see shift in pathogen community largely driven by changes in intestinal parasites (ordering consistent with above).

```{r, descriptive_stats_comparison, echo=FALSE}
newdf2<-newdf[-c(newdf$name=="FIV"),]
newdf2$prevneg<-NA;  newdf2$prevpos<-NA
for (i in 1:length(newdf2$parasite)){
    newdf2$prevneg[i]<-get_prev(dataneg[,colnames(dataneg) == newdf2$parasite[i]])
    newdf2$prevpos[i]<-get_prev(datapos[,colnames(datapos) == newdf2$parasite[i]])
    }
virus2<-newdf2[newdf2$type=="virus",]
gut2<-newdf2[newdf2$type=="gut",]
blood2<-newdf2[newdf2$type=="bloodborne",]

par(mfrow=c(1,2), mar=c(4,5,4,2)+0.1)
barplot2(height=c(virus2$prevneg[order(virus2$prev, decreasing=FALSE)], 
                  gut2$prevneg[order(gut2$prev, decreasing=FALSE)], 
                  blood2$prevneg[order(blood2$prev, decreasing=FALSE)]), 
         names.arg=c(as.character(virus2$name[order(virus2$prev, decreasing=FALSE)]), 
                  as.character(gut2$name[order(gut2$prev, decreasing=FALSE)]), 
                  as.character(blood2$name[order(blood2$prev, decreasing=FALSE)])),
         col=c(as.character(virus2$col[order(virus2$prev, decreasing=FALSE)]), 
                  as.character(gut2$col[order(gut2$prev, decreasing=FALSE)]), 
                  as.character(blood2$col[order(blood2$prev, decreasing=FALSE)])),
         horiz=TRUE, las=1, main="FIV negative ", xlab="Prevalence", cex.names= 0.8)
barplot2(height=c(virus2$prevpos[order(virus2$prevpos, decreasing=FALSE)], 
                  gut2$prevpos[order(gut2$prevpos, decreasing=FALSE)], 
                  blood2$prevpos[order(blood2$prevpos, decreasing=FALSE)]), 
         names.arg=c(as.character(virus2$name[order(virus2$prevpos, decreasing=FALSE)]), 
                  as.character(gut2$name[order(gut2$prevpos, decreasing=FALSE)]), 
                  as.character(blood2$name[order(blood2$prevpos, decreasing=FALSE)])),
         col=c(as.character(virus2$col[order(virus2$prevpos, decreasing=FALSE)]), 
                  as.character(gut2$col[order(gut2$prevpos, decreasing=FALSE)]), 
                  as.character(blood2$col[order(blood2$prevpos, decreasing=FALSE)])),
         horiz=TRUE, las=1, main="FIV positive ", xlab="Prevalence", cex.names= 0.8)
```


```{r, data_prep, include=FALSE}
##################################################
##################################################
# Construct networks: parasite, lion and bipartite networks
# networks constructed in calculate_net_and_node_stats
# network results are saved to file so code is suppresed here, read in from csv
# bipartite networks still need sorted!!!!!!!!
##################################################
##################################################

##################################################
# all animals, FIV+ animals, FIV- animals
##################################################
# need networks from dataset without 'OTHER', 'BABESIA'
drop <- c('THEILERIABABESIA', 'OTHER', 'BABESA')
alldata <- alldata[, !names(alldata) %in% drop]
plotdata <- plotdata[, !names(plotdata) %in% drop]
all<-make_edgelist(alldata)
all2<-make_all_matrix(alldata)  # for making parasite monoparte matrix
all3<-make_all_lionmatrix(alldata) 
allb<-make_all_bipartite_matrix(alldata)
all_parnet<- tcrossprod(t(all2))  # nodes=parasites; edges=number of shared hosts, symmetric
all_lionnet<-tcrossprod(t(all3))  # nodes=lions; edges=number of shared parasites, symmetric
#calculate_net_and_node_stats(all_parnet, name="allparasitenetwork")
#calculate_net_and_node_stats(all_lionnet, name="alllionnetwork")

##################################################
#, FIV+ animals, FIV- animals
##################################################
temp<-NA
dataneg <- dataneg[, !names(dataneg) %in% drop]
FIVneg<- make_edgelist(dataneg)
FIVneg2<-make_matrix(dataneg); FIVneg3<-make_lionmatrix(dataneg)
colnames(FIVneg2) <- colnames(plotdata[-1])
FIVneg_parnet<- tcrossprod(t(FIVneg2))  # nodes=parasites; edges=number of shared hosts, sym
FIVneg_lionnet<-tcrossprod(t(FIVneg3))  # nodes=lions; edges=number of shared parasites, sym
FIVneg_binet<- make_bipartite_matrix(dataneg) # nodes = lions and parasites

datapos <- datapos[, !names(datapos) %in% drop]
FIVpos<-make_edgelist(datapos)
FIVpos2<-make_matrix(datapos); FIVpos3<-make_lionmatrix(datapos)
colnames(FIVpos2) <- colnames(plotdata[-1])
FIVpos_parnet<- tcrossprod(t(FIVpos2))  # nodes=parasites; edges=number of shared hosts, sym
FIVpos_lionnet<-tcrossprod(t(FIVpos3))  # nodes=lions; edges=number of shared parasites, sym
FIVpos_binet<- make_bipartite_matrix(datapos)

#calculate_net_and_node_stats(FIVpos_parnet, name="FIVposparasitenetwork")
#calculate_net_and_node_stats(FIVneg_parnet, name="FIVnegparasitenetwork")
#calculate_net_and_node_stats(FIVpos_lionnet, name="FIVposlionnetwork")
#calculate_net_and_node_stats(FIVneg_lionnet, name="FIVneglionnetwork")

####binets here! bipartite node statistics calculated in association with figures

##################################################
# In animals with high, very high, medium, and low FIV status (Not Saved)
##################################################
#FIVvh<- make_edgelist(alldata[alldata$FIVSTATUS=="Very High",])
#FIV2vh<-make_matrix(alldata[alldata$FIVSTATUS=="Very High",])
#colnames(FIV2vh) <- colnames(plotdata[-1])
#FIV3vh<-make_lionmatrix(alldata[alldata$FIVSTATUS=="Very High",])
#parnet_FIVvh<-tcrossprod(t(FIV2vh))  # nodes=parasites; edges=number of shared hosts
#lionnet_FIVvh<-tcrossprod(t(FIV3vh))
####FIVvh_binet<- make_bipartite_matrix(alldata[alldata$FIVSTATUS=="Very High",])


#FIVhigh<-make_edgelist(alldata[alldata$FIVSTATUS=="High",])
#FIV2h<-make_matrix(alldata[alldata$FIVSTATUS=="High",])
#colnames(FIV2h) <- colnames(plotdata[-1])
#parnet_FIVh<-tcrossprod(t(FIV2h))
#FIV3h<-make_lionmatrix(alldata[alldata$FIVSTATUS=="High",])
#lionnet_FIVh<-tcrossprod(t(FIV3h))
####FIVh_binet<- make_bipartite_matrix(alldata[alldata$FIVSTATUS=="High",])


#FIVmed<-make_edgelist(alldata[alldata$FIVSTATUS=="Medium",])
#FIV2med<-make_matrix(alldata[alldata$FIVSTATUS=="Medium",])
#colnames(FIV2med) <- colnames(plotdata[-1])
#parnet_FIVmed<-tcrossprod(t(FIV2med))
#FIV3med<-make_lionmatrix(alldata[alldata$FIVSTATUS=="Medium",])
#lionnet_FIVmed<-tcrossprod(t(FIV3med))
#####FIVmed_binet<- make_bipartite_matrix(alldata[alldata$FIVSTATUS=="Medium",])

#FIVlow<-make_edgelist(alldata[alldata$FIVSTATUS=="Low",])
#FIV2low<-make_matrix(alldata[alldata$FIVSTATUS=="Low",])
#colnames(FIV2low) <- colnames(plotdata[-1])
#parnet_FIVlow<-tcrossprod(t(FIV2low))
#FIV3low<-make_lionmatrix(alldata[alldata$FIVSTATUS=="Low",])
#lionnet_FIVlow<-tcrossprod(t(FIV3low))
####FIVlow_binet<- make_bipartite_matrix(alldata[alldata$FIVSTATUS=="Low",])

#calculate_net_and_node_stats(parnet_FIVvh, name="FIV_vh_parasitenetwork")
#calculate_net_and_node_stats(parnet_FIVh, name="FIV_high_parasitenetwork")
#calculate_net_and_node_stats(parnet_FIVmed, name="FIV_med_parasitenetwork")
#calculate_net_and_node_stats(parnet_FIVlow, name="FIV_low_parasitenetwork")

#calculate_net_and_node_stats(lionnet_FIVvh, name="FIV_vh_lionnetwork")
#calculate_net_and_node_stats(lionnet_FIVh, name="FIV_high_lionnetwork")
#calculate_net_and_node_stats(lionnet_FIVmed, name="FIV_med_lionnetwork")
#calculate_net_and_node_stats(lionnet_FIVlow, name="FIV_low_lionnetwork")

# Summarize parasite networks
##################################################
pall<- read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/net_stats_allparasitenetwork.csv")
pneg<- read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/net_stats_FIVnegparasitenetwork.csv")
ppos<- read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/net_stats_FIVposparasitenetwork.csv")
parasitenet<-rbind(pall[c(-1,-6, -8)], pneg[c(-1,-6, -8)], ppos[c(-1,-6, -8)])
rownames(parasitenet)<-c("Overall_Network", "FIV_negative", "FIV_positive")

# Summarize lion networks
##################################################
lall<-read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/net_stats_alllionnetwork.csv")
lneg<-read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/net_stats_FIVneglionnetwork.csv")
lpos<-read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/net_stats_FIVposlionnetwork.csv")
lionnet<-rbind(lall[c(-1,-6, -8)], lneg[c(-1,-6, -8)], lpos[c(-1,-6, -8)])
rownames(lionnet)<-c("Overall_Network", "FIV_negative", "FIV_positive")
# Summarize bipartite networks
##################################################
#bipartitenet<-
```


## Network statistics
Below I consider three abstractions of the host-parastie community.  A "parasite network", a "host network", and a bipartite network.  Likely I will use the later, but they may all be useful abstractions. 

### Network statistics pt 1: Parasite network
For the parasite network, we define nodes as parasite/pathogen species.  An edge connects two nodes if the pathogens share the same host. Edges are weighted by the number of shared hosts. 
All network and node statistics were calculated with igraph (for monopartite networks).  In this context, we can interpret the following network statistics: 

* Number of nodes: the number of parasites observed   
* Mean Degree (Unweighted): the average number of pathogens each pathogen is connected to by sharing a host. 
* Diameter: The maximum number of steps in the set of shortest paths between all parasite pairs.  This is a measure of connectedness- if you are one parasite, how quickly can you get to all the parasites.
* Transitivity: The ratio of the number of triangles and the number of connected triples in the graph.  Transitivity ranges from 0 to 1, with higher values indicating more connected subgraphs. It is a measure of clustering (high transitivity values mean you have clusters of pathogens that co-occur togeter- this will be interesting to see which ones are which!) 
* Weighted Assortivity: The correlation between a parasites degree and the degree of the parasites connected to it.  Assortivity ranges from -1 to 1, with positive values indicating that nodes with high or low numbers of hosts interact mostly with nodes with similar degree values.  I interpret negative assortivity values as generalists pathogens are found with specialists.

```{r}
parasitenet
```

### Network statistics pt 2: Lion network
For the lion network, we define nodes as lions and edges as sharing the same pathogen/parasite. Edges are weighted by the number of shared parasites. The same definitions apply: 

* Number of nodes: the number of lions observed.  By comparing FIV+ and FIV- networks we can evaluate if the number of lions with FIV is greater than the number of lions without FIV. 
* Mean Degree (Weighted): the average number of pathogens per host.  FIV negative lions share fewer parasites/pathogens with other lions than FIV positive hosts.  This gets more exciting when you compare their distributions!  
* Diameter: The maximum number of steps in the set of shortest paths between all lion pairs.  This is a measure of connectedness- if you are one lion, how quickly can you get to all the other lions.
* Transitivity: The ratio of the number of triangles and the number of connected triples in the graph.  Transitivity ranges from 0 to 1, with higher values indicating more connected subgraphs. This measure shows that both FIV+ and FIV- networks are consistently really highly connected, so just reflects the fact that co-infections are really common. 
* Weighted Assortivity: The correlation between a parasites degree and the degree of the parasites connected to it.  Assortivity ranges from -1 to 1, with positive values indicating that nodes with high or low numbers of hosts interact mostly with nodes with similar degree values.  Here FIV negative lions with high numbers of parasites/pathogens interact mostly wiht lions with few numbers of pathogens.

```{r}
lionnet
```


### Parasite and lion node statistics
Node statistics are properties of each node.  For example, node statistics from the lion network tell you about how well connected or not each lion is based on its shared pathogens.  Node statistics are great because they can be regressed againsed age, sex, condition. I calcuated the following monopartite statistics and provide definitions based on the lion network: 

* Weighted Degree: The number of lions connected to the focal lion by sharing a parasite.  If lions share 5 parasites, this value is 5. 
* Unwieghted Degree: The number of lions connected to the focal lion (unweighted)
* Betweenness: The number of shortest paths between any two lions that go through the focal lion.  This is measure of how central the lion is in the network. 
* Closeness: The number of steps required to reach every other lion.  This is another measure of centrality. 
* Transitivity: For the focal lion, this is the ratio of the triangles connected to the vertex and the triples centered on the vertex.  I find this confusing and prefer the global measure. 
* Average nearest neighbor degree: The average number of lions connected to the immediate neighbors of the focal lion. 

Degree distributions:

For each parasite, unweighted degree reflects the number of other parasites the focal parasite co-occurs with in at least one hosts.  In FIV + lions, the unweighted degree distribution (left) is shifted right, suggesting that the pathogen community is overall more connected. 

For each parasite, weighted degree reflects the number of other parasites the focal parasite co-occurs with summed over all hosts.  The weighted degree distribution (right) follows similar patterns as the unweighted degree distribution. 

This reflects the fact that in FIV + lions, 90% (19/21) of parasites co-occur with ten or more other parasites compared to 10% (2/21) in FIV - lions.  (NOTE: This could be because there are fewer FIV - lions but we can bootstrap test that!)
```{r, degree_distributions_parasite, echo=FALSE}
# plot histogram of degree distribution for FIV + and FIV -
pall<- read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/node_stats_allparasitenetwork.csv")
pneg<- read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/node_stats_FIVnegparasitenetwork.csv")
ppos<- read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/node_stats_FIVposparasitenetwork.csv")

wtbreaks <- seq(0, 500, 50)
unbreaks <- seq(0, 20, 2)

negwt <- hist(pneg$DegreeWt , breaks = wtbreaks , plot = FALSE)
poswt <- hist(ppos$DegreeWt , breaks = wtbreaks , plot = FALSE)
negun <- hist(pneg$DegreeUnWt , breaks = unbreaks , plot = FALSE)
posun <- hist(ppos$DegreeUnWt , breaks = unbreaks , plot = FALSE)

par(mfrow = c(1,2), mar= c(4, 4, 3, 0.5))
# unweighted
plot(negun$mids[1:(length(negun$counts)-2)], negun$counts[1:(length(negun$counts)-2)], xlim = c(0, 20), ylim= c(0, 7), 
     xlab = "Unweighted degree", ylab= "Frequency", las= 1, 
     type = "b", pch= 19, lty = 1, lwd = 1, tck = -0.025, bty = "n", 
     main= "Parasite network")
lines(posun$mids, posun$counts, lwd = 1, lty = 3)
points(posun$mids, posun$counts, pch= 21, lty = 3)

# weighted
par(mar= c(4, 2, 3, 0.5))
plot(negwt$mids[1:length(negwt$counts[negwt$counts > 0])], negwt$counts[1:length(negwt$counts[negwt$counts > 0])], xlim = c(0, 450), ylim= c(0, 20), 
     xlab = "Weighted degree", ylab= "", las= 1, 
     type = "b", pch= 19, lty = 1, lwd = 1, tck = -0.025, bty = "n")
lines(poswt$mids[1:(length(negwt$mids)- 1)], poswt$counts[1:(length(negwt$mids)- 1)], lwd = 1, lty = 3)
points(poswt$mids[1:(length(negwt$mids)- 1)], poswt$counts[1:(length(negwt$mids)- 1)], pch= 21, lty = 3)

legend("topright", c("FIV -", "FIV +"), lty=c(1, 3), pch=c(19, 21), lwd=1, bty="n")
```


For each lion in the lion network, unweighted degree reflects the number of other lions the focal lion is connected to by sharing any parasite while weighted degree is summed over each parasite.  In FIV + lions, ?

```{r, degree_distributions_lion, echo=FALSE}
# plot histogram of degree distribution for FIV + and FIV -
pall<- read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/node_stats_alllionnetwork.csv")
pneg<- read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/node_stats_FIVneglionnetwork.csv")
ppos<- read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/node_stats_FIVposlionnetwork.csv")

wtbreaks <- seq(0, 400, 50)
unbreaks <- seq(0, 90, 10)

negwt <- hist(pneg$DegreeWt , breaks = wtbreaks , plot = FALSE)
poswt <- hist(ppos$DegreeWt , breaks = wtbreaks , plot = FALSE)
negun <- hist(pneg$DegreeUnWt , breaks = unbreaks , plot = FALSE)
posun <- hist(ppos$DegreeUnWt , breaks = unbreaks , plot = FALSE)

par(mfrow = c(1,2), mar= c(4, 4, 3, 0.5))
# unweighted
plot(negun$mids[1:length(negun$counts[negun$counts> 0])], negun$counts[1:length(negun$counts[negun$counts> 0])], xlim = c(0, 85), ylim= c(0, 50), 
     xlab = "Unweighted degree", ylab= "Frequency", las= 1, 
     type = "b", pch= 19, lty = 1, lwd = 1, tck = -0.025, bty = "n", 
     main = "Lion network")
lines(posun$mids, posun$counts, lwd = 1, lty = 3)
points(posun$mids, posun$counts, pch= 21, lty = 3)

# weighted
par(mar= c(4, 2, 3, 0.5))
plot(negwt$mids[1:length(negwt$counts[negwt$counts > 0])], negwt$counts[1:length(negwt$counts[negwt$counts > 0])], xlim = c(0, 450), ylim= c(0, 30), 
     xlab = "Weighted degree", ylab= "", las= 1, 
     type = "b", pch= 19, lty = 1, lwd = 1, tck = -0.025, bty = "n")
lines(poswt$mids, poswt$counts, lwd = 1, lty = 3)
points(poswt$mids, poswt$counts, pch= 21, lty = 3)

legend("topright", c("FIV -", "FIV +"), lty=c(1, 3), pch=c(19, 21), lwd=1, bty="n")
```


### Network statistics pt 3: Bipartite network

## Visualization
Virus nodes are green, gut parasite nodes are salmon, blue nodes are blood borne pathogens

Note: the big green dot is FIV.
```{r, visualization_all, fig.width=10, fig.height=4, echo=FALSE}
##################################################
##################################################
# Visualize bipartite network
##################################################
##################################################
make_bipart_hive_plot(allb, datatype="all", demogdata=alldata, save_nodedf=FALSE, name="nosave")


```

Network in FIV positive hosts
Note: Three largest circles are bloodbornes (CDV, TANNAE, TBICORNIS).  This is probably artifical from being a seroprevlaence measure.

```{r, visualization_FIVpos, echo=FALSE}
##################################################
##################################################
# Visualize FIV+ bipartite network
##################################################
##################################################
make_bipart_hive_plot(FIVpos_binet, datatype="all", demogdata=alldata, 
                      save_nodedf=FALSE, name="nosave")
#make_bipart_hive_plot(FIVpos_binet, datatype="all", demogdata=alldata, 
#                      save_nodedf=TRUE, name="binet_FIVpos")
```

Network in FIV negative hosts

```{r, visualization_FIVneg, echo=FALSE}
##################################################
##################################################
# Visualize FIV+ bipartite network
##################################################
##################################################
make_bipart_hive_plot(FIVneg_binet, datatype="subset", demogdata=alldata, 
                      save_nodedf=FALSE, name="nosave")
#make_bipart_hive_plot(FIVneg_binet, datatype="subset", demogdata=alldata, 
#                      save_nodedf=TRUE, name="binet_FIVneg")
```

## Analysis: Do degree distribution in FIV+ and FIV - lions differ

The mean parasite richness in FIV- lions is 4 compared to 5 in FIV+ lions.  The variance in FIV- lions is 2.1 vs. 4.9 in FIV+ lions.  Overall, there does not appear to be a clear shift towards higher or lower parasite richness among hosts.  There are more hosts in the FIV
Is that driven by more than sample size? 

```{r, degree_distributions_bipartite, echo=FALSE}
# plot histogram of degree distribution for FIV + and FIV -
bineg<- read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/nodedfbinet_FIVneg.csv")
binegl<- bineg[bineg$axis==1,]
bipos<- read.csv("~/Documents/postdoc_buffology/HB-lion_coinfection_network/lion_coinfection_networks_files/nodedfbinet_FIVpos.csv")
biposl<- bipos[bipos$axis==1,]


breaks <- seq(0, 10, 1)
# Note: Value divided by maximum value in the network...
poswt <- hist(biposl$degree_nonorm , breaks = breaks , plot = FALSE)
negwt <- hist(binegl$degree_nonorm , breaks = breaks , plot = FALSE)

# weighted
plot(negwt$mids, negwt$counts, xlim = c(0, 10), ylim= c(0, 17), 
     xlab = "Bipartite Degree (Parasite richness)", ylab= "Number of lions", las= 1, 
     type = "b", pch= 19, lty = 1, lwd = 1, tck = -0.025, bty = "n")
lines(poswt$mids, poswt$counts, lwd = 1, lty = 3)
points(poswt$mids, poswt$counts, pch= 21, lty = 3)

legend("topright", c("FIV -", "FIV +"), lty=c(1, 3), pch=c(19, 21), lwd=1, bty="n")
```


## Analysis: Do we  see higher centrality values in older lions and males?

```{r, age_sex_patterns, echo=FALSE}
temp<-as.data.frame(tapply(binegl$degree, list(binegl$malefemale, binegl$agecat), mean))
n<- temp[,-2]
n[is.na(n)]<-0
barplot2(as.matrix(n), beside=TRUE, col=c("darkslategray2", "darkslategray"), ylab= "Weighted Degree", main= "FIV- lions")
legend("topright", legend= c("Female", "Male"), fill=c("darkslategray2", "darkslategray"), cex=0.7, bty="n")
temp<- as.data.frame(tapply(biposl$degree, list(biposl$malefemale, biposl$agecat), mean))
p<- temp[,-4]
barplot2(as.matrix(p), beside=TRUE, col=c("darkslategray2", "darkslategray"), ylab= "Weighted Degree", main= "FIV+ lions", las=1, names.arg =c("Cub", "Geriatric", "Juv", "Prime", "SubAd"))

#tapply(binegl$degree, list(binegl$malefemale, binegl$agecat), sd)
#tapply(biposl$degree, list(biposl$malefemale, biposl$agecat), sd)


temp<-as.data.frame(tapply(binegl$betweenness, list(binegl$malefemale, binegl$agecat), mean))
n<- temp[,-2]
n[is.na(n)]<-0
barplot2(as.matrix(n), beside=TRUE, col=c("darkslategray2", "darkslategray"), ylab= "Betweenness Centrality", main= "FIV- lions")
legend("topright", legend= c("Female", "Male"), fill=c("darkslategray2", "darkslategray"), cex=0.7, bty="n")
temp<- as.data.frame(tapply(biposl$betweenness, list(biposl$malefemale, biposl$agecat), mean))
p<- temp[,-4]
barplot2(as.matrix(p), beside=TRUE, col=c("darkslategray2", "darkslategray"), ylab= "Betweenness Centrality", main= "FIV+ lions", las=1, names.arg =c("Cub", "Geriatric", "Juv", "Prime", "SubAd"))

tapply(binegl$degree, list(binegl$malefemale, binegl$agecat), sd)
tapply(biposl$degree, list(biposl$malefemale, biposl$agecat), sd)



```

## Analysis: Do we see lower centrality measures in animals with both hookworms and FIV?



