---
title: "Lion Coinfection Networks"
author: "Erin Gorsich"
date: "January 13, 2016"
output: html_document
---

```{r, data_readin, include=FALSE}
###########################################################
# read in HB's data and packages and scripts code
###########################################################
setwd("~/Documents/postdoc_buffology/HB-lion_coinfection_network")
alldata<-read.csv("COINCLIQ.csv")
dataneg<-alldata[alldata$FIV=="Negative",]
datapos<-alldata[alldata$FIV=="Positive",]
plotdata<-alldata[,c(11:35)]
library(lattice)  
library(igraph)  # tried bigraph but not avaliable
library(gplots)
library(HiveR)
 library(grid)
#####################
# Functions: There are three script files required to run this script
source("prep_data_to_matrix.R")   # functions that groom raw data into network matricies
source("calculate_net_and_node_stats.R")  # functions that calculate network statistics
source("make_bipart_hive_plot.R")   
source("mod.edge2HPD.R")
# see: Patterns of interactions of a large fish–parasite network in a tropical floodplain by Lima et al. 2012
```
##Summary statistics  
Plot of overall patogen prevalence ordered by type and prevalence
```{r, descriptive_stats, echo=FALSE}
get_prev<-function(dat) {length(dat[dat=="Positive"])/length(dat)}
temp<-apply(alldata[,c(11:35)], 2, get_prev)
gut = c("ASCARIDS", "TAPES", "HOOKS", "COCCIDIA", "TOXO")
bloodborne = c("ERLICHIAANAPLASMA", "THEILERIABABESIA", "BABESA", 
               "BFELIS", "BLEO", "BMICROTI", "BLENGUA", "TBICORNIS", 
               "HEPATOZOON", "TANNAE", "BCANIS", "BROSSI", "BVOGELI")
virus = c("FIV", "CDV", "FPV", "CALICI", "CORONA")

newdf<-data.frame(parasite=c(virus, gut, bloodborne), type=c(rep("virus", length(virus)), rep("gut", length(gut)), rep("bloodborne", length(bloodborne)) ), prev=NA, col= c(rep("darkseagreen", length(virus)), rep("darksalmon", length(gut)), rep("lightblue3", length(bloodborne))) )

for (i in 1:length(newdf$parasite)){
    temp<- alldata[,colnames(alldata) == as.character(newdf$parasite[i])]
    newdf$prev[i]<- length(temp[temp=="Positive"])/length(temp)
    rm(temp)
}
newdf$parasite<-as.character(newdf$parasite)
newdf$name<-newdf$parasite
newdf$name[11]<-"ERLANAP"
newdf$name[12]<-"THEILERIA"
newdf$name[19]<-"HEPATO"

virus<-newdf[newdf$type=="virus",]
gut<-newdf[newdf$type=="gut",]
blood<-newdf[newdf$type=="bloodborne",]

par(mar=c(4,5,4,2)+0.1)
barplot2(height=c(virus$prev[order(virus$prev, decreasing=FALSE)], 
                  gut$prev[order(gut$prev, decreasing=FALSE)], 
                  blood$prev[order(blood$prev, decreasing=FALSE)]), 
         names.arg=c(as.character(virus$name[order(virus$prev, decreasing=FALSE)]), 
                  as.character(gut$name[order(gut$prev, decreasing=FALSE)]), 
                  as.character(blood$name[order(blood$prev, decreasing=FALSE)])),
         col=c(as.character(virus$col[order(virus$prev, decreasing=FALSE)]), 
                  as.character(gut$col[order(gut$prev, decreasing=FALSE)]), 
                  as.character(blood$col[order(blood$prev, decreasing=FALSE)])),
         horiz=TRUE, las=1)
```


Plot of prevalence in FIV+ and FIV- lions shows a shift in pathogen community (ordering consistent with above)
```{r, descriptive_stats_comparison, echo=FALSE}
newdf2<-newdf[-1,]
newdf2$prevneg<-NA;  newdf2$prevpos<-NA
for (i in 1:length(newdf2$parasite)){
    newdf2$prevneg[i]<-get_prev(dataneg[,colnames(dataneg) == newdf2$parasite[i]])
    newdf2$prevpos[i]<-get_prev(datapos[,colnames(datapos) == newdf2$parasite[i]])
    }
virus2<-newdf2[newdf2$type=="virus",]
gut2<-newdf2[newdf2$type=="gut",]
blood2<-newdf2[newdf2$type=="bloodborne",]

par(mfrow=c(1,2), mar=c(4,5,4,2)+0.1)
barplot2(height=c(virus2$prevneg[order(virus2$prev, decreasing=FALSE)], 
                  gut2$prevneg[order(gut2$prev, decreasing=FALSE)], 
                  blood2$prevneg[order(blood2$prev, decreasing=FALSE)]), 
         names.arg=c(as.character(virus2$name[order(virus2$prev, decreasing=FALSE)]), 
                  as.character(gut2$name[order(gut2$prev, decreasing=FALSE)]), 
                  as.character(blood2$name[order(blood2$prev, decreasing=FALSE)])),
         col=c(as.character(virus2$col[order(virus2$prev, decreasing=FALSE)]), 
                  as.character(gut2$col[order(gut2$prev, decreasing=FALSE)]), 
                  as.character(blood2$col[order(blood2$prev, decreasing=FALSE)])),
         horiz=TRUE, las=1, main="FIV negative ", xlab="Prevalence")
barplot2(height=c(virus2$prevpos[order(virus2$prevpos, decreasing=FALSE)], 
                  gut2$prevpos[order(gut2$prevpos, decreasing=FALSE)], 
                  blood2$prevpos[order(blood2$prevpos, decreasing=FALSE)]), 
         names.arg=c(as.character(virus2$name[order(virus2$prevpos, decreasing=FALSE)]), 
                  as.character(gut2$name[order(gut2$prevpos, decreasing=FALSE)]), 
                  as.character(blood2$name[order(blood2$prevpos, decreasing=FALSE)])),
         col=c(as.character(virus2$col[order(virus2$prevpos, decreasing=FALSE)]), 
                  as.character(gut2$col[order(gut2$prevpos, decreasing=FALSE)]), 
                  as.character(blood2$col[order(blood2$prevpos, decreasing=FALSE)])),
         horiz=TRUE, las=1, main="FIV positive ", xlab="Prevalence")
```


```{r, data_prep, include=FALSE}
##################################################
##################################################
# Construct networks: parasite, lion and bipartite networks
# networks constructed in calculate_net_and_node_stats
# network results are saved to file so code is suppresed here, read in from csv
# bipartite networks still need sorted!!!!!!!!
##################################################
##################################################

# all animals, FIV+ animals, FIV- animals
##################################################
#temp<-NA
all<-make_edgelist(alldata)
all2<-make_all_matrix(alldata)  # for making parasite monoparte matrix
all3<-make_all_lionmatrix(alldata) 
allb<-make_all_bipartite_matrix(alldata)
all_parnet<- tcrossprod(t(all2))  # nodes=parasites; edges=number of shared hosts, symmetric
all_lionnet<-tcrossprod(t(all3))  # nodes=lions; edges=number of shared parasites, symmetric
#calculate_net_and_node_stats(all_parnet, name="allparasitenetwork")
#calculate_net_and_node_stats(all_lionnet, name="alllionnetwork")
####calculate_bipartite_net_and_node_stats()

#, FIV+ animals, FIV- animals
##################################################
temp<-NA
FIVneg<- make_edgelist(dataneg)
FIVneg2<-make_matrix(dataneg); FIVneg3<-make_lionmatrix(dataneg)
colnames(FIVneg2) <- colnames(plotdata[-1])
FIVneg_parnet<- tcrossprod(t(FIVneg2))  # nodes=parasites; edges=number of shared hosts, symmetric
FIVneg_lionnet<-tcrossprod(t(FIVneg3))  # nodes=lions; edges=number of shared parasites, symmetric
FIVneg_binet<- make_bipartite_matrix(dataneg)

FIVpos<-make_edgelist(datapos)
FIVpos2<-make_matrix(datapos); FIVpos3<-make_lionmatrix(datapos)
colnames(FIVpos2) <- colnames(plotdata[-1])
FIVpos_parnet<- tcrossprod(t(FIVpos2))  # nodes=parasites; edges=number of shared hosts, symmetric
FIVpos_lionnet<-tcrossprod(t(FIVpos3))  # nodes=lions; edges=number of shared parasites, symmetric
FIVpos_binet<- make_bipartite_matrix(datapos)

#calculate_net_and_node_stats(FIVpos_parnet, name="FIVposparasitenetwork")
#calculate_net_and_node_stats(FIVneg_parnet, name="FIVnegparasitenetwork")
#calculate_net_and_node_stats(FIVpos_lionnet, name="FIVposlionnetwork")
#calculate_net_and_node_stats(FIVneg_lionnet, name="FIVneglionnetwork")
####binets here!


# In animals with high, very high, medium, and low FIV status
##################################################
#FIVvh<- make_edgelist(alldata[alldata$FIVSTATUS=="Very High",])
#FIV2vh<-make_matrix(alldata[alldata$FIVSTATUS=="Very High",])
#colnames(FIV2vh) <- colnames(plotdata[-1])
#FIV3vh<-make_lionmatrix(alldata[alldata$FIVSTATUS=="Very High",])
#parnet_FIVvh<-tcrossprod(t(FIV2vh))  # nodes=parasites; edges=number of shared hosts
#lionnet_FIVvh<-tcrossprod(t(FIV3vh))
####FIVvh_binet<- make_bipartite_matrix(alldata[alldata$FIVSTATUS=="Very High",])


#FIVhigh<-make_edgelist(alldata[alldata$FIVSTATUS=="High",])
#FIV2h<-make_matrix(alldata[alldata$FIVSTATUS=="High",])
#colnames(FIV2h) <- colnames(plotdata[-1])
#parnet_FIVh<-tcrossprod(t(FIV2h))
#FIV3h<-make_lionmatrix(alldata[alldata$FIVSTATUS=="High",])
#lionnet_FIVh<-tcrossprod(t(FIV3h))
#FIVh_binet<- make_bipartite_matrix(alldata[alldata$FIVSTATUS=="High",])


#FIVmed<-make_edgelist(alldata[alldata$FIVSTATUS=="Medium",])
#FIV2med<-make_matrix(alldata[alldata$FIVSTATUS=="Medium",])
#colnames(FIV2med) <- colnames(plotdata[-1])
#parnet_FIVmed<-tcrossprod(t(FIV2med))
#FIV3med<-make_lionmatrix(alldata[alldata$FIVSTATUS=="Medium",])
#lionnet_FIVmed<-tcrossprod(t(FIV3med))
#FIVmed_binet<- make_bipartite_matrix(alldata[alldata$FIVSTATUS=="Medium",])

#FIVlow<-make_edgelist(alldata[alldata$FIVSTATUS=="Low",])
#FIV2low<-make_matrix(alldata[alldata$FIVSTATUS=="Low",])
#colnames(FIV2low) <- colnames(plotdata[-1])
#parnet_FIVlow<-tcrossprod(t(FIV2low))
#FIV3low<-make_lionmatrix(alldata[alldata$FIVSTATUS=="Low",])
#lionnet_FIVlow<-tcrossprod(t(FIV3low))
#FIVlow_binet<- make_bipartite_matrix(alldata[alldata$FIVSTATUS=="Low",])

#calculate_net_and_node_stats(parnet_FIVvh, name="FIV_vh_parasitenetwork")
#calculate_net_and_node_stats(parnet_FIVh, name="FIV_high_parasitenetwork")
#calculate_net_and_node_stats(parnet_FIVmed, name="FIV_med_parasitenetwork")
#calculate_net_and_node_stats(parnet_FIVlow, name="FIV_low_parasitenetwork")

#calculate_net_and_node_stats(lionnet_FIVvh, name="FIV_vh_lionnetwork")
#calculate_net_and_node_stats(lionnet_FIVh, name="FIV_high_lionnetwork")
#calculate_net_and_node_stats(lionnet_FIVmed, name="FIV_med_lionnetwork")
#calculate_net_and_node_stats(lionnet_FIVlow, name="FIV_low_lionnetwork")

# Summarize parasite networks
##################################################
pall<- read.csv("net_stats_allparasitenetwork.csv")
pneg<- read.csv("net_stats_FIVnegparasitenetwork.csv")
ppos<- read.csv("net_stats_FIVposparasitenetwork.csv")
parasitenet<-rbind(pall[c(-1,-6, -8)], pneg[c(-1,-6, -8)], ppos[c(-1,-6, -8)])
rownames(parasitenet)<-c("Overall_Network", "FIV_negative", "FIV_positive")

# Summarize lion networks
##################################################
lall<-read.csv("net_stats_alllionnetwork.csv")
lneg<-read.csv("net_stats_FIVneglionnetwork.csv")
lpos<-read.csv("net_stats_FIVposlionnetwork.csv")
lionnet<-rbind(lall[c(-1,-6, -8)], lneg[c(-1,-6, -8)], lpos[c(-1,-6, -8)])
rownames(lionnet)<-c("Overall_Network", "FIV_negative", "FIV_positive")
# Summarize bipartite networks
##################################################
#bipartitenet<-
```


##Network statistics
For the parasite network, we define nodes as parasite/pathogen species and edges as sharing the same host. Edges are weighted by the number of shared hosts. 
All network and node statistics were calculated with igraph
```{r}
parasitenet
```
Number of nodes: the number of parasites observed  
Mean degree: The average number of shared hosts per pathogen.   
*Diameter: The maximum number of steps in the set of shortest paths between all parasite pairs. (STILL NEED TO SORT OUT!)*   
Transitivity: The ratio of the number of triangles and the number of connected triples in the graph.  Transitivity ranges from 0 to 1, with higher values indicating more connected subgraphs. (High transitivity values mean you have clusters that co-occur togeter- this will be interesting to see which ones are which!!!!!!!!!!!)  
Assortivity: The correlation between a parasites degree and the degree of the parasites connected to it.  Assortivity ranges from -1 to 1, with positive values indicating that nodes with high or low numbers of hosts interact mostly with nodes with similar degree values.  (I interpret negative assortivity values as generalists pathogens are found with specialists)  

Network properties: For the lion network, we define nodes as lions and edges as sharing the same pathogen/parasite. Edges are weighted by the number of shared parasites. 
```{r}
lionnet
```
Number of nodes: the number of lions with FIV is greater than the number of lions without FIV (matching prevlaence graph)   
Mean degree: FIV negative lions share fewer parasites/pathogens with other lions than FIV positive hosts.    
Transitivity: consistently really highly connected regardless of FIV+ or negative.  
Assortivity: FIV negative lions with high numbers of parasites/pathogens interact mostly wiht lions with few numbers of pathogens.  



## Visualization
Virus nodes are green, gut parasite nodes are salmon, blue nodes are blood borne pathogens
```{r, visualization_all, fig.width=10, fig.height=4, echo=FALSE}
##################################################
##################################################
# Visualize bipartite network
##################################################
##################################################
make_bipart_hive_plot(allb, datatype="all", demogdata=alldata, save_nodedf=FALSE, name="nosave")

```

```{r, visualization_FIVpos, echo=FALSE}
##################################################
##################################################
# Visualize FIV+ bipartite network
##################################################
##################################################
make_bipart_hive_plot(FIVpos_binet, datatype="FIV", demogdata=alldata, save_nodedf=FALSE, name="nosave")

```


```{r, visualization_FIVneg, echo=FALSE}
##################################################
##################################################
# Visualize FIV+ bipartite network
##################################################
##################################################
# NEED TO SPECIFY SIZES OF DIFFERNET LION VS. PARAISTE SUBSETS- form negdata
#make_bipart_hive_plot(FIVneg_binet, datatype="FIV", demogdata=alldata, save_nodedf=FALSE, name="nosave")

```

